Differential invariant signatures for planar Lie group transformations of images

### 2019-09-11 paper/newpaper.tex
now with compilation

\begin{equation}
\left( \begin{array}f_x \\ f_y \end{array} \right) = \left( \begin{array} \cos \theta & \sin \theta \\ - \sin \theta & \cos \theta \end{array} \right) \left( \begin{array} \bar f_{\bar x} \\ \bar f_{\bar y} \end{array} \right).
\end{equation}

>>>>

\begin{equation}
\left( \begin{array}{c} f_x \\ f_y \end{array} \right) = \left( \begin{array}{cc} \cos \theta & \sin \theta \\ - \sin \theta & \cos \theta \end{array} \right) \left( \begin{array}{c} \bar f_{\bar x} \\ \bar f_{\bar y} \end{array} \right).
\end{equation}
